The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
fix vander wal

## Keywords
<!-- TODO: is this the final list ? -->
Social network analysis, Landscape ecology, Movement ecology, Space use

@@

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO:
something broken here?? --> Further, for social interactions or associations to
occur individuals must share space, and thus have overlapping home ranges
[@Vander_Wal_2013]. In the context of the social environment, home range overlap
is an example of how animals share space over coarser spatial and temporal
scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
scales spatially and temporally, it remains unclear whether coarser scales of
sociality, including social association and home range overlap, vary predictably
with social interaction [@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a]. <!--
Farine references comes out as D.R. Farine 2015 -->

>>>>

## Keywords
Social network analysis, Landscape ecology, Movement ecology, Space use

@@

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or associations to
occur individuals must share space, and thus have overlapping home ranges
[@Vander_Wal_2013]. In the context of the social environment, home range overlap
is an example of how animals share space over coarser spatial and temporal
scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
scales spatially and temporally, it remains unclear whether coarser scales of
sociality, including social association and home range overlap, vary predictably
with social interaction [@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a]. <!--
Farine references comes out as D.R. Farine 2015 -->
